Title Text

### 2014-04-07 paper.tex
Type updated
Talking may be helpful if my emails seem confusing.

When it comes to types MoA keeps things very simple. There are two
types: arrays and scalars. Furthermore, scalars and singleton arrays
are identified.
% scalars are arrays from an MoA and Psi Calculus perspective.

>>>>

When it comes to types MoA keeps things very simple. There is just one
type, arrays.  Scalars are arrays;  their shape is the empty vector. Consequently, we have the identify given any array, $\xi$
\[( \iota (\rho \xi)  )\psi \xi \equiv \xi\]
That is, given an array's shape, all indices can be generated to index the entire array.
% scalars are arrays from an MoA and Psi Calculus perspective.
